Deep Reinforcement Learning for Conservation Decisions

### 2021-05-14 manuscript/manuscript.Rmd
Finishing training and tuning

@@

## Training and tuning an agent
<!-- Maybe rename this as Training and Tuning an Agent -> how to practically get an agent up and running -->
<!-- Ecologist job to build environment; CS job to build agent 
      Ok so talk about this in very general terms
      selecting an agent, why you might want to use different ones
-->
Training a deep, model-free agent on an environment involves allowing the agent to interact with the environment for thousands or even millions of time steps.

In practice, the general process for attaining a good performing agent is to tune model hyperparameters then train an agent using the best hyperparameters. 
Hyperparameters refer to the parameters in a RL algorithm that are not directly learned during the training process. <!-- better to define before using in opening sentence.  -->
For example, a weight in the neural network is a model parameter, but the number of hidden layers in the neural network is a hyperparameter.
Since the optimal hyperparameters cannot be found analytically, tuning should be done to find a good-performing set of hyperparameters.
The process of tuning can be automated through standard multi-dimensional optimization approaches: proposing new combinations of hyperparameters, training an agent, and examining the resulting performance.
Since one round of training can be time intensive, hyperparameter tuning, which consists of usually numerous rounds of training, can be particularly time intensive.

<!--
A rapidly growing set of material for learning about deep reinforcement learning is now freely available.... (maybe just describe this in the appendix)
-->

>>>>

## Training and tuning an agent
<!-- Maybe rename this as Training and Tuning an Agent -> how to practically get an agent up and running -->
<!-- Ecologist job to build environment; CS job to build agent 
      Ok so talk about this in very general terms
      selecting an agent, why you might want to use different ones
-->
Training a deep, model-free agent on an environment involves allowing the agent to interact with the environment for thousands or even millions of time steps.
The training period involves a trial and error process whereby the agent will perform an action and then receive feedback from the environment in the form of a reward. 
This process will repeat until the environment transitions to a terminal state, after which the environment will reset to some starting condition.
According to the algorithm that the agent follows, the agent will explore different state-action trajectories and use its experience to improve its policy.
The amount of time needed for an agent to learn high reward yielding behavior cannot be predetermined and depends on a host of factors including the amount of dedicated compute, the simulation complexity of the environment, model complexity of the agent and more.
Yet, overall, it has been well established that deep, model-free RL agents tend to be very sample inefficient [@cite], so it is recommended to provide a generous training budget for these agents.

Hyperparameters refer to the parameters in a deep, RL algorithm that are not directly learned during the training process.
For example, a weight in an agent's neural network is not a hyperparameter, but the number of hidden layers in this network would be a hyperparameter.
Since the optimal hyperparameters cannot be found analytically [@cite], it is necessary to find a good-performing set of hyperparameters in a process called hyperparameter tuning.
Hyperparameter tuning consists of the following general steps in repetition: proposing a new set of hyperparameters, training an agent with this set, then examining the resulting performance.
This procedure can be automated through standard multi-dimensional optimization approaches. 
Since one round of training can be time intensive, hyperparameter tuning, which consists of usually numerous rounds of training, can be particularly time intensive.
Hyperparameter tuning, however, is a necessary step in evaluating the performance of an algorithm and should be a standard component of any RL workflow.

@@
